### 2011-02-10 paper/introduction.tex
shrinking figs
foo
cut intro

\acmFig{robot_close.jpg}{1}{The quadruped robot. The translucent parts
  were created with 3D-printing technology. Videos of the gaits
  evolved for this robot can be viewed online~\cite{quadratotWeb}.}

Gaits for walking robots are often designed with some explicit or
implicit goal in mind.  For some applications, the design criteria may
be obvious --- perhaps the robot needs to move as quickly or as
efficiently as possible --- but other times the objective is more complicated,
requiring simultaneous optimization of several desired traits, each
with its own relative importance.  The different combinations of desired traits and the relative weight placed on each can produce drastically different gaits.    For example, Honda's Asimo
\cite{chestnutt2006footstep} and Boston Dynamic's Big Dog \cite{raibert2008bigdog} both require
gaits that are relatively quick, power efficient, and robust to
changing terrain, but they vary widely in the importance placed
on each attribute.  Big Dog's gait is optimized for much more difficult terrain than Asimo's, resulting in a gait of a completely different form.

Once the design goals are decided upon, gaits may be obtained by one
of several methods.  Gaits may be designed manually by an expert, as
for Asimo and Big Dog \cite{chestnutt2006footstep, raibert2008bigdog}.
Alternately, they may be learned through repeated trial and
evaluation.  Learned gaits offer several advantages over manually
designed gaits.  Automatically learning gaits can save valuable
engineering time and can allow customization of gaits to a particular
robot and its unique actuators.  Most importantly, in many cases
learned gaits can outperform manually designed
gaits~\cite{hornby2005autonomous, valsalam2008modular}.

>>>>

\acmFig{robot_close.jpg}{.8}{The quadruped robot. The translucent parts
  were created with 3D-printing technology. Videos of the gaits
  evolved for this robot can be viewed at www.anonymous.url.}

%Gaits for walking robots are often designed with some explicit or
%implicit goal in mind.  For some applications, the design criteria may
%be obvious --- perhaps the robot needs to move as quickly or as
%efficiently as possible --- but other times the objective is more complicated,
%requiring simultaneous optimization of several desired traits, each
%with its own relative importance.  The different combinations of desired traits and the relative weight placed on each can produce drastically different gaits.    For example, Honda's Asimo
%\cite{chestnutt2006footstep} and Boston Dynamic's Big Dog \cite{raibert2008bigdog} both require
%gaits that are relatively quick, power efficient, and robust to
%changing terrain, but they vary widely in the importance placed
%on each attribute.  Big Dog's gait is optimized for much more difficult terrain than Asimo's, resulting in a gait of a completely different form.

%Once the design goals are decided upon, gaits may be obtained by one

Legged robots have the potential to access many types of terrain
unsuitable for wheeled robots, but doing so requires the creation of a
gait specifying how the robot is to walk.  Gaits may be designed
by one of several methods: either manually by an expert or
automatically through repeated trial and evaluation.  Learned gaits
offer several advantages over manually designed gaits.  Automatically
learning gaits can save valuable engineering time and can allow
customization of gaits to a particular robot and its unique actuators.
Most importantly, in many cases learned gaits can outperform manually
designed gaits~\cite{hornby2005autonomous, valsalam2008modular}.
